Overlay databank unlocks data-driven analyses of biomolecules for all

### 2023-05-12 CoverLetter2.tex

Please find enclosed our manuscript titled
{\it NMRlipids Databank makes data-driven analysis of biomembrane properties accessible for all}, which we would like to submit for your consideration to be published as a Resource in \textit{Nature Methods}.

@@

By providing rapid open access to simulation data and automaticly  assessing
%ranking of simulations based on 
their quality against experiments, the NMRlipids Databank holds immediate practical relevance for the broad basic research community studying membranes in life sciences --- ranging from molecular cell biology to biomedical applications such as lipid nanoparticles. Even more importantly, the programmable interface for flexible implementation of data-driven and machine learning applications will advance new biological applications of MD simulation data.
We validate the practical relevance of the NMRlipids Databank here by successfully analysing how anisotropic diffusion of water and cholesterol flip-flop depend on membrane properties. Both of these processes are highly relevant for magnetic resonance imaging (MRI), pharmacokinetics, lipid trafficking, and regulating membrane properties of cellular membranes --- yet their timescales are beyond the scope of standard MD simulation investigations.

@@

We see that the NMRlipids Databank has both immediate and long term impact for a broad interdisciplinary audience of academic and industry researchers across
%at different fields in
life sciences: from biophysics and biochemistry to biology, biotechnology and biomedicine. Consequently, we trust our manuscript to fulfill the high standards for publication in %the \textit{Resource} section of
\textit{Nature Methods}.\\

>>>>

Please find enclosed our manuscript titled
{\it NMRlipids Databank makes data-driven analysis of biomembrane properties accessible for all}, which we would like to submit for your consideration to be published as a Resource in \textit{ Nature Structural \& Molecular Biology}.

@@

By providing rapid open access to simulation data and automaticly assessing their quality against experiments, the NMRlipids Databank holds immediate practical relevance for the broad basic research community studying membranes in life sciences --- ranging from molecular cell biology to biomedical applications such as lipid nanoparticles. Even more importantly, the programmable interface for flexible implementation of data-driven and machine learning applications will advance new biological applications of MD simulation data. We validate the practical relevance of the NMRlipids Databank on functional and mechanistic understanding of biological process 
%how molecular components in a work together
by successfully analysing how anisotropic diffusion of water and cholesterol flip-flop depend on membrane properties. Both of these processes are highly relevant for magnetic resonance imaging (MRI), pharmacokinetics, lipid trafficking, and regulating membrane properties of cellular membranes --- yet their timescales are beyond the scope of standard MD simulation investigations.

@@

We see that the NMRlipids Databank has both immediate and long term impact for a broad interdisciplinary audience of academic and industry researchers across life sciences: from biophysics and biochemistry to biology, biotechnology and biomedicine. Feedback on our first submission to \textit{Nature Methods} states that the manuscript is of interest on this field of research. Therefore, we trust our manuscript to fulfill the high standards for publication in \textit{ Nature Structural \& Molecular Biology}.
.\\
